%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Modified Atallah - One Page Two Column Resume
% LaTeX Template
% Version 1.0 (07/04/2020)
%
% Author
% Ahmad Atallah

%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
\usepackage[utf8]{inputenc}
\usepackage{eurosym}
\usepackage{progressbar}
\usepackage{graphicx}    % For layout adjustments
\usepackage[document]{ragged2e}


\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Ahmad}{Atallah}{ \urlstyle{same}\href{https://atallahsan.cc}
\vspace{1pt}
\\
{\bf atallahsan.cc} \textbullet{}
\href{mailto:me@atallahsan.cc}{\bf me@atallahsan.cc} \textbullet{} \href{tel: +491744745520}{\bf +491744745520} \textbullet{} \urlstyle{same}\href{https://github.com/ahmadatallah}{\bf Github} \textbullet{}
\urlstyle{same}\href{https://twitter.com/ahmadatallah}{\bf Twitter}}

\begin{minipage}[t]{0.63\textwidth}\end{minipage}%
\hfill
\begin{minipage}[t]{0.35\textwidth}{\Large\textit{Frontend engineer and artist}}\end{minipage}
\vspace{8pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.63\textwidth}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\sectionsep
\runsubsection{Hashcards}
\descript{— Owner }
\location{Sep \textbf{2025} – Present}
\subsectionsep{}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developing a free spaced repetition flashcard app, currently on its 10th release.
\item Optimizing UX based on real gathered user feedback.
\item Sharing knowledge on FSRS (Free Spaced Repetition Scheduler).
\end{tightemize}
\sectionsep
\vspace{4pt}

\runsubsection{Getsafe}
\descript{— Sr Software Engineer (Frontend) }
\location{Apr \textbf{2023} – Present | Remote, Germany}
\subsectionsep{}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Launching and maintaining high quality insurance products serving +500K customers in Germany, France, Austria and (previously) UK
\item Developing and improving buying flows/funnels for various insurance products with high conversion rate, backed by user sessions and a data persistence layer
\item Maintaining a monorepo hosting multiple apps and shared packages across web and mobile, with Expo and EAS Build/Update pipelines for native releases
\item Shipping OTA updates to thousands of customers, enabling rapid iteration and hotfixes without app store releases
\item Building a backend-for-frontend (BFF) layer to aggregate and tailor API responses for client-specific needs
\item Configuring and maintaining a Sanity CMS for products, clients, and platforms enabling seamless editing and rich content experience
\item Bootstrapping a rich content personalization datasource tailored for the native mobile app
\item Delivering insurance product features to mobile apps including documents, payments, and policy details
\item Resolving customer support tickets with proper regression and postmortems
\item Actively contributing to the Getsafe design system, aligning component tokens and documentation across platforms

\end{tightemize}
\sectionsep
\vspace{4pt}

\runsubsection{Aeditive GmbH}
\descript{— Sr Software Engineer (Fullstack) }
\location{Mar \textbf{2022} – Apr \textbf{2023} | Hamburg, Germany}
\subsectionsep{}
\begin{tightemize}
\item Bootstrapped and actively developed a new SaaS backoffice solution platform for concrete 3D printing.
\item Developed and designed a UI components library tailored to work in sync with 3D rendering
\end{tightemize}
\sectionsep
\vspace{4pt}
\runsubsection{Swvl Business}
\descript{— Sr. Software Engineer I (Frontend) }
\location{Jul \textbf{2021} – Mar \textbf{2022} | Cairo, Egypt}
\subsectionsep{}
\begin{tightemize}
\item Lead the frontend development team of the company for its B2B scope.
\item Maintain SWVL web design system.
\item Guide and onboard new comers.
\end{tightemize}
\sectionsep
\vspace{4pt}

\runsubsection{Swvl}
\descript{— Software Engineer II (Frontend)}
\location{Dec \textbf{2018} – Jun \textbf{2021} | Cairo, Egypt}
\subsectionsep{}
\begin{tightemize}
\item Worked on developing the company's administration dashboard and website.
\item Initiated and released the company's business dashboards.
\item Developed, and published a design system components packages on npm.
\end{tightemize}
\sectionsep
\vspace{4pt}

\runsubsection{Qobra}
\descript{— Software Engineer (Frontend)}
\location{Dec \textbf{2019} - Aug \textbf{2020 } | Remote}
\subsectionsep{}
\begin{tightemize}
\item Started the core product desktop app with electron.
\item Streamlined project's boilerplate to speed up development, with support for multiple tabs, shared state, and others.
\end{tightemize}
\sectionsep
\vspace{4pt}

\runsubsection{Millensys}
\descript{— Software Engineer (Visualization)}
\location{Feb - Dec \textbf{2018} | Alexandria, Egypt}
\subsectionsep{}
\begin{tightemize}
\item Worked in the medical imaging team with OpenJPEG, LEADTOOLS, Windows API, OpenGL, canvas drawing, advanced image processing techniques, 2D and 3D visualization.
\item Assigned to advanced DICOM viewer project (web based, and Desktop), reporting tool and others.
\end{tightemize}
\sectionsep
\vspace{4pt}

\runsubsection{Cairo University}
\descript{— Engineering Graduate (Medical Visualization)}
\location{Nov 2016 - Jul \textbf{2017} | Cairo, Egypt}
\subsectionsep{}
\begin{tightemize}
\item Visualization Desktop App for fast 2-projection 2D-3D registration that assists in patient positioning process during radiation oncology treatment procedures.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}
\subsectionsep{}
\textbf{Cairo University}— Bachelor of System and Biomedical Engineering
\location{Jul \textbf{2012 } - \textbf{2017} | Cairo, Egypt}
\subsectionsep{}
\textbf{Thesis} GPU-Based Visualization Application for 2-Projection 2D-3D Image Registration In Radiation Oncology
\sectionsep

\section{Activities}
\subsectionsep{}
\textbf{Generative Artist} \\
I'm also passionate about generative art and design topics in my free time for fun, like generative design with CSS using \href{https://components.ai/}{components.ai}
, typography, and art.
\sectionsep

\textbf{Amateur photographer}\\
\textbf{Yet, sometimes Blender render-er}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{minipage}%
\hfill
\begin{minipage}[t]{0.35\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\sectionsep
\subsection{AI}
\subsectionsep{}
Working with AI across the development cycle — structured prompting, agentic workflows, and tool integrations. Drawing on a consolidated engineering skillset to critically review and verify what models produce.

\vspace{4pt}
\noindent
\begin{flushleft}
\begin{tabular}{@{}l@{\hspace{16pt}}l@{}}
\textbf{Coding:} & \textbf{Design:} \\[2pt]
Claude Code \textbullet{} Cursor \textbullet{} ChatGPT & Pencil \textbullet{} Figma \\[6pt]
\textbf{Agents:} & \textbf{Infra:} \\[2pt]
Mastra \textbullet{} Vercel AI SDK \textbullet{} LangChain & MCP Servers \textbullet{} Streaming APIs \\
\end{tabular}
\end{flushleft}
\sectionsep
\subsection{Programming}
\subsectionsep{}
\location{\textbf{Over 250k lines:}}
\noindent
\makebox[\textwidth][l]{%
    TypeScript, Javascript
}%
\makebox[0.0cm][r]{%
    \progressbar{0.95}
}

\subsectionsep{}
\location{\textbf{Over 6000 lines:}}
\noindent
\makebox[\textwidth][l]{%
   NodeJS, Astro
}%
\makebox[0.0cm][r]{%
    \progressbar{0.75}
}
\noindent
\makebox[\textwidth][l]{%
    Python
}%
\makebox[0.0cm][r]{%
    \progressbar{0.55}
}

\subsectionsep{}
\location{\textbf{Over 3000 lines:}}
\noindent
\makebox[\textwidth][l]{%
    Lua, Shell
}%
\makebox[0.0cm][r]{%
    \progressbar{0.45}
}

\subsectionsep{}
\location{\textbf{Familiar:}}
\noindent
\makebox[\textwidth][l]{%
    Haskell, Pascal, C/C++, Scala
}%
\makebox[0.0cm][r]{%
    \progressbar{0.25}
}

\subsectionsep{}
\location{\textbf{Currently learning:}}
\noindent
\makebox[\textwidth][l]{%
    Lean, Zig
}%
\makebox[0.0cm][r]{%
    \progressbar{0.15}
}
\sectionsep

\subsection{Development}
\subsectionsep
\textbf{\faCaretRight \hspace{2pt} Client Libraries} —
\noindent
\makebox[\textwidth][l]{%
    React \& ReactNative
}%
\makebox[0.0cm][r]{%
    \progressbar{0.85}
}
\noindent
\makebox[\textwidth][l]{%
    Vue
}%
\subsectionsep
\makebox[0.0cm][r]{%
    \progressbar{0.45}
}

\textbf{\faCaretRight \hspace{2pt} Frameworks} —
\noindent
\makebox[\textwidth][l]{%
    Next.JS with SSR \& RSC
}%
\makebox[0.0cm][r]{%
    \progressbar{0.75}
}
\noindent
\makebox[\textwidth][l]{%
    Gatsby with SSR \& SSG
}%
\makebox[0.0cm][r]{%
    \progressbar{0.75}
}
\noindent
\makebox[\textwidth][l]{%
    Expo
}%
\makebox[0.0cm][r]{%
    \progressbar{0.75}
}
\noindent
\makebox[\textwidth][l]{%
    Express
}%
\makebox[0.0cm][r]{%
    \progressbar{0.7}
}
\noindent
\makebox[\textwidth][l]{%
    Remix, Angular, \& Serverless
}%
\subsectionsep
\makebox[0.0cm][r]{%
    \progressbar{0.6}
}
\vspace{3pt}
\textbf{\faCaretRight \hspace{2pt} Editors} — \\
\noindent
\makebox[\textwidth][l]{%
    VSCode/Cursor \& Vim \& Neovim
}%
\subsectionsep
\makebox[0.0cm][r]{%
    \progressbar{0.8}
}
\vspace{2pt}
\textbf{\faCaretRight \hspace{2pt} Animation} — \\
\noindent
\makebox[\textwidth][l]{%
    Rive, Motion, Reanimated \& Moti
}%
\subsectionsep
\makebox[0.0cm][r]{%
    \progressbar{0.8}
}
\vspace{2pt}
\textbf{\faCaretRight \hspace{2pt} Build/task Runners} — \\
\noindent
\makebox[\textwidth][l]{%
    Webpack, Rollup, Babel, Turbo, \& Metro
}%
\subsectionsep
\makebox[0.0cm][r]{%
    \progressbar{0.8}
}
\vspace{3pt}
\textbf{\faCaretRight \hspace{2pt} VCS \& CI/CD} —\\
\noindent
\makebox[\textwidth][l]{%
    Git, CircleCI, Github Actions, Heroku, \& EAS
}%
\makebox[0.0cm][r]{%
    \progressbar{0.8}
}

\makebox[\textwidth][l]{%
  Bitrise, SVN, \&  Jenkins
}%
\subsectionsep
\makebox[0.0cm][r]{%
    \progressbar{0.3}
}
\vspace{2pt}
\textbf{\faCaretRight \hspace{2pt} Content Management} — \\
\noindent
\makebox[\textwidth][l]{%
    Sanity
}%
\makebox[0.0cm][r]{%
    \progressbar{0.8}
}
\noindent
\makebox[\textwidth][l]{%
    Contentful \& Strapi
}%
\subsectionsep
\makebox[0.0cm][r]{%
    \progressbar{0.5}
}
\vspace{2pt}
\textbf{\faCaretRight \hspace{2pt} Styling} — \\
\noindent
\makebox[\textwidth][l]{%
CSS, Tailwind, Tachyons \& Theme-UI
}%
\makebox[0.0cm][r]{%
    \progressbar{0.9}
}
\noindent
\makebox[\textwidth][l]{%
Styled Components \& Emotion
}%
\makebox[0.0cm][r]{%
    \progressbar{0.8}
}
\noindent
\makebox[\textwidth][l]{%
CSS Modules \& SCSS
}%
\subsectionsep
\makebox[0.0cm][r]{%
    \progressbar{0.6}
}
\vspace{2pt}
\textbf{\faCaretRight \hspace{2pt} Design Systems} — \\
\noindent{\small\textit{Tooling:}}\\
\noindent
\makebox[\textwidth][l]{%
Storybook \& Chromatic
}%
\makebox[0.0cm][r]{%
    \progressbar{0.85}
}
\noindent
\makebox[\textwidth][l]{%
Radix UI \& shadcn/ui
}%
\makebox[0.0cm][r]{%
    \progressbar{0.8}
}
\noindent{\small\textit{Platforms:}}\\
\noindent
\makebox[\textwidth][l]{%
Penpot
}%
\makebox[0.0cm][r]{%
    \progressbar{0.5}
}
\noindent
\makebox[\textwidth][l]{%
Zeroheight
}%
\subsectionsep
\makebox[0.0cm][r]{%
    \progressbar{0.3}
}
\vspace{2pt}
\textbf{\faCaretRight \hspace{2pt} Templating} — \\
\noindent
\makebox[\textwidth][l]{%
HTML,  JSX, MD \& MDX
}%
\makebox[0.0cm][r]{%
    \progressbar{0.8}
}

\noindent
\makebox[\textwidth][l]{%
 Handlbars
}%
\subsectionsep
\makebox[0.0cm][r]{%
    \progressbar{0.7}
}
\vspace{2pt}
\textbf{\faCaretRight \hspace{2pt} Testing} — \\
\noindent
\makebox[\textwidth][l]{%
 Jest, React testing library, MSW \& Cypress
}%
\makebox[0.0cm][r]{%
    \progressbar{0.85}
}
\noindent
\makebox[\textwidth][l]{%
 Puppeteer, Maestro
}%
\subsectionsep
\makebox[0.0cm][r]{%
    \progressbar{0.7}
}
\vspace{2pt}
\textbf{\faCaretRight \hspace{2pt} Utilities} — \\
\noindent
\makebox[\textwidth][l]{%
Lodash, ts-pattern, React form \& i18next
}%
\makebox[0.0cm][r]{%
    \progressbar{0.9}
}
\noindent
\makebox[\textwidth][l]{%
Runtypes, Zod, Socket.IO, Ramda \& fp-ts
}%
\subsectionsep
\makebox[0.0cm][r]{%
    \progressbar{0.95}
}
\vspace{2pt}
\textbf{\faCaretRight \hspace{2pt} State Machines} — \\
\noindent
\makebox[\textwidth][l]{%
 Redux toolkit, xState
}%
\makebox[0.0cm][r]{%
    \progressbar{0.9}
}
\noindent
\makebox[\textwidth][l]{%
  Signal
}%
\subsectionsep
\makebox[0.0cm][r]{%
    \progressbar{0.7}
}
\vspace{2pt}
\textbf{\faCaretRight \hspace{2pt} Querying \& APIs} — \\
\noindent
\makebox[\textwidth][l]{%
  REST, tRPC \& SSE
}%
\makebox[0.0cm][r]{%
    \progressbar{0.9}
}
\noindent
\makebox[\textwidth][l]{%
GraphQl, GROQ, \& React Query
}%
\subsectionsep
\makebox[0.0cm][r]{%
    \progressbar{0.85}
}

\textbf{\faCaretRight \hspace{2pt} Database} — \\
\noindent
\makebox[\textwidth][l]{%
 Instant
}%
\subsectionsep
\makebox[0.0cm][r]{%
    \progressbar{0.7}
}
\vspace{2pt}
\textbf{\faCaretRight \hspace{2pt} Infrastructure} — \\
\noindent
\makebox[\textwidth][l]{%
 AWS, Docker/compose, \& Heroku
}%
\makebox[0.0cm][r]{%
    \progressbar{0.85}
}
\noindent
\makebox[\textwidth][l]{%
Qovery \& Terraform
}%
\subsectionsep
\makebox[0.0cm][r]{%
    \progressbar{0.7}
}
\vspace{2pt}
\textbf{\faCaretRight \hspace{2pt} Observability} — \\
\noindent
\makebox[\textwidth][l]{%
Mixpanel, Datadog \& Sentry
}%
\makebox[0.0cm][r]{%
    \progressbar{0.85}
}
\noindent
\makebox[\textwidth][l]{%
Periscope \& Hotjar
}%
\subsectionsep
\makebox[0.0cm][r]{%
    \progressbar{0.65}
}
\textbf{\faCaretRight \hspace{2pt} Messaging} — \\
\noindent
\makebox[\textwidth][l]{%
Sendgrid \& Customer.io
}%
\makebox[0.0cm][r]{%
    \progressbar{0.75}
}
\noindent
\makebox[\textwidth][l]{%
 Fastmail
}%
\makebox[0.0cm][r]{%
    \progressbar{0.85}
}
\end{minipage}%
\end{document}
\documentclass[]{article}

